---
main_topsize: 0.1 #percent coverage of the poster
main_bottomsize: 0.03
#ESSENTIALS
title: '**Design of a Spatial Depopulation Risk Indicator**'
author:
  - name: '**Isidro Hidalgo Arellano & Gema Fernández-Avilés Calderón** Isidro.Hidalgo@uclm.es - Gema.FAviles@uclm.es'
    main: true
Way:
main_findings:
  - "**Depopulation Risk in Castilla-La Mancha**"
logoleft_name: PNG/UCLM.png
logoright_name: PNG/RepoGitHub.png
column_numbers: 1
poster_height: "46.8in"
poster_width: "33.1in"
css: particularidades.css
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    highlight: espresso
    number_sections: false
bibliography: XIJornadasDoctorado.bib
link-citations: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```
:::: {.gridContainer}

::: {.col_1}

# Introduction

Did you know that some areas of Castilla-La Mancha have `a lower population density than Siberia`?


# Objectives

-   [**General**](): Construction of a Spatial Depopulation Risk Index using spatial Principal Component Analysis
-   [**Secondaries**]():
    -   to detect spatial dependence in depopulation in Castilla-La Mancha
    -   to calculate the range of this spatial dependence
    -   to extract the index from the principal component and to scale it

# Methods

Spatial dependence is checked with Moran's I:

$$
I= \frac{N}{\sum _{i}\sum _{j} w_{ij}} \frac {\sum _{i}\sum _{j} w_{ij} (X_i - \bar{X}) (X_j - \bar{X})} {\sum _{i} (X_i - \bar{X})^2}
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd.

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/brentthorne/posterdown/wiki).

***Now on to the results!***

:::

::: {.col_2}

# Results

:::::: {.columns}
::: {.column width="50%"}

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

:::

::: {.column width="50%"}

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

:::
::::::


# References

Jombart, T.; Devillard, S.; Dufour, A.-B.; Pontier, D. *Revealing cryptic spatial patterns in genetic variability by a new multivariate method*, Heredity, 101 (2008), 92-103.


:::

::::


